% Appendix A: complete specification of the headline calibrator.
% Every constant here matches src/conformal/panel_hierarchical.py; the
% exact-replay tests in tests/test_theory_identity.py enforce agreement.

\appendix

\section{Complete algorithm specification}\label{app:algorithm}

This appendix specifies the headline calibrator exactly as run, with
every constant. The same constants are used in every experiment in the
paper; none is tuned per dataset, per period, or per result. The
reference implementation and an exact-replay test that reproduces the
recursion below from the calibrator's outputs at $10^{-10}$ tolerance
accompany the replication package.

\paragraph{Fixed constants.} Nominal level $\alpha = 0.10$ two-sided
unless stated ($a = \alpha/2$ per side; the one-sided head uses
$a = \alpha$); warmup $T_0 = 100$ trading days; score scale window
$w = 250$ days with minimum history 50 days; regime count $K = 4$ with
VIX-percentile bin edges $(0.5, 0.8, 0.95)$ on a trailing 750-day
window; expert rate grid $\mathcal{G} = (0.0005, 0.001, 0.002, 0.004,
0.008, 0.016, 0.032, 0.064)$, a dyadic ladder with $E = 8$ elements;
aggregation rate $\lambda = 5.0$; uniform-mixing coefficient
$\sigma_{\mathrm{mix}} = 0.01$; corrector rate
$\eta_{\mathrm{corr}} = 0.002$. All rates are per stock-day
(per-observation steps).

\paragraph{Scores and scale.} For stock $i$ with point forecast
$m_{i,t}$ and outcome $y_{i,t}$, the residual is
$r_{i,t} = y_{i,t} - m_{i,t}$ and the scale is the lagged trailing
robust estimate
\[
  \hat\sigma_{i,t} \;=\; 1.4826 \cdot \operatorname{median}_{\tau \in
  [t-w,\, t-1]} \bigl| r_{i,\tau} -
  \operatorname{median}_{[t-w,\,t-1]} r_{i,\cdot} \bigr| ,
\]
computed over the most recent $w$ residuals, requiring at least 50, and
treated as missing when zero. The score is
$s_{i,t} = r_{i,t} / \hat\sigma_{i,t}$; stock-days with missing scores
are excluded. The upper side tracks $s_{i,t}$ and the lower side tracks
$-s_{i,t}$ with identical, independent machinery; we write one side.

\paragraph{Timeline and membership.} One explicit timeline governs every
index in the paper. At the close of day $t-1$: the state vector is
computed from information through that close; the resulting one-hot VIX
bin and the thresholds as of the end of day $t-1$ determine the interval
issued for outcome day $t$. At the close of day $t$: the outcome is
observed and all updates run. Rows are indexed by the \emph{outcome}
day, so $\pi_t \in \{0,1\}^K$, the regime attached to outcome day $t$,
is computed from information through the prior close --- these are two
descriptions of the same convention, not two conventions. ``Day 1 after
regime entry'' is the first outcome day whose prior-close state is
classified stress. If the state variable is unavailable, the
implementation falls back to uniform $\pi_t = (1/K, \ldots, 1/K)$; such
a day would be soft-membership and hence outside the hard-regime setting
of Proposition~2. This never occurs in the evaluation window, so every
evaluated day is hard one-hot and the guarantee applies as stated.

\paragraph{Initialization.} Let $\mathcal{W}$ be the first $T_0$ days.
All expert thresholds initialize at the empirical $(1-a)$-quantile of
warmup scores, $Q_1(k, j) = \widehat{F}^{-1}_{\mathcal{W}}(1 - a)$ for
all $k, j$; log-weights $L_1(k, j) = 0$; correctors $c_1(k) = 0$. No
predictions during $\mathcal{W}$ enter any reported result.

\paragraph{Daily recursion.} On day $t$ with active regime $k_t$
(the $k$ with $\pi_t(k) = 1$), stocks $\mathcal{I}_t$, $n_t =
|\mathcal{I}_t|$, and $\tau = 1 - a$:
\begin{enumerate}
\item \emph{Issue.} Normalized weights $w_t(k, j) \propto \exp L_t(k,
j)$. Issued threshold $\bar q_t = \sum_j w_t(k_t, j)\, Q_t(k_t, j) +
c_t(k_t)$. Stock $i$ receives the upper bound $m_{i,t} + \bar
q_t\,\hat\sigma_{i,t}$ (lower bound analogously from the lower-side
tracker).
\item \emph{Observe} scores $s_{i,t}$, $i \in \mathcal{I}_t$.
\item \emph{Expert updates} (own-threshold errors), for every $j$ and
$k = k_t$ only:
\[
  Q_{t+1}(k, j) = Q_t(k, j) + \eta_j \Bigl( \textstyle\sum_{i}
  \mathbf{1}\{ s_{i,t} > Q_t(k, j) \} - a\, n_t \Bigr).
\]
\item \emph{Weight updates} on mean pinball loss
$\ell_t(j) = n_t^{-1} \sum_i \rho_\tau\bigl( s_{i,t} - Q_t(k_t, j)
\bigr)$ with $\rho_\tau(u) = u(\tau - \mathbf{1}\{u < 0\})$:
\[
  L_{t+1}(k_t, j) = L_t(k_t, j) - \lambda\, \ell_t(j),
\]
followed by membership-gated uniform mixing on the probability scale,
$w \leftarrow (1 - \sigma_{\mathrm{mix}})\, w +
\sigma_{\mathrm{mix}} / E$, stored back as log-weights. Mixing is gated
by $\pi_t$ so a rare regime's weights evolve only in its own regime
time.
\item \emph{Corrector update} (issued-threshold errors):
\[
  c_{t+1}(k_t) = c_t(k_t) + \eta_{\mathrm{corr}} \Bigl(
  \textstyle\sum_i \mathbf{1}\{ s_{i,t} > \bar q_t \} - a\, n_t \Bigr).
\]
\item All quantities for $k \ne k_t$ are unchanged. Stocks absent on
day $t$ (delisted or missing data) simply do not contribute terms; no
imputation is performed.
\end{enumerate}

\paragraph{Reductions.} A single-element grid with
$\eta_{\mathrm{corr}} = 0$ reduces the recursion exactly to the
fixed-rate update of eq.~\eqref{eq:update} (regression-tested to
$10^{-12}$); $K = 1$ gives pooled marginal tracking; restricting
$\mathcal{I}_t$ to one stock gives per-stock Mondrian tracking. These
reductions are the ablation arms of Section~\ref{sec:ablations}.

\paragraph{VaR head.} The one-sided head applies the identical recursion
with $a = \alpha \in \{0.05, 0.01\}$ and one (upper) threshold to
standardized return losses: with forecast volatility
$\sigma^{\mathrm{pred}}_{i,t} = \exp(m_{i,t}/2)$ from the log-variance
forecast, the score is $z_{i,t+1} = -\,\mathrm{ret}_{i,t+1} /
\sigma^{\mathrm{pred}}_{i,t}$ (a loss exceedance in volatility units;
the prediction at day $t$ is scored against the \emph{next} day's
return), and the VaR forecast is
$\mathrm{VaR}^{(1-\alpha)}_{i,t+1} = \bar q_t\,
\sigma^{\mathrm{pred}}_{i,t}$. Benchmark methods that produce return
quantiles directly (GARCH-$t$, CAViaR) are converted to the same $z$
units so all methods share one exceedance test.
