\section{Data and evaluation design}\label{sec:data}

\paragraph{Universe.} The panel is the top 100 US companies by market
capitalization, reconstituted each January from CRSP point-in-time data:
common shares (share codes 10/11) on NYSE, AMEX, or NASDAQ, capitalization
aggregated across share classes at the company level as of the prior
December month-end. Companies that later delist remain in the panel for
the years they qualified (Lehman Brothers' final observation is
2008-09-17), so no selection on survival contaminates the sample. Over
2005--2025 the universe contains 223 distinct companies (mean turnover
10.6 names per year; 42 members later delisted), for 519{,}843 stock-days.
Identity is keyed by CRSP PERMNO end-to-end, avoiding recycled-ticker
mismatches by construction.

\paragraph{Realized volatility.} Daily realized variances are the Chicago
Booth Risk Lab estimates computed from TAQ high-frequency data: QMLE
volatilities \citep{xiu2010quasi, da2021moving} alongside 5-minute
subsampled realized variance, retrieved by PERMNO. We forecast log
5-minute RV; results are insensitive to the estimator choice. Corporate
action duplicates are deduplicated with uniqueness asserts, and a
delisting-aware guard verifies that every history terminating early
matches a CRSP delisting event.

\paragraph{State variables.} Market state uses FRED series (VIX, term
spread, Moody's credit spread) and CBOE term-structure indices (VIX9D),
all as available at the close of day $t$; per-stock and market RV
percentiles are trailing 750-day ranks. Cross-sectional dispersion enters
with a one-day lag.

\paragraph{Walk-forward protocol.} All forecasters are trained on
expanding windows with quarterly refits and a hard assertion that
$\max(\text{train dates}) < \min(\text{test dates})$; calibration is fully
online with a 100-day warmup; evaluation covers 2010--2025. Regime slices
for evaluation are trailing VIX-percentile bins: calm ($\le$0.5), normal
(0.5--0.8), elevated (0.8--0.95), stress ($>$0.95); the stress slice
contains 14{,}085 stock-days spanning 2011, 2015, 2018, 2020, 2022, 2024,
and 2025 episodes. Method comparisons are computed on the common sample on
which all ten methods are defined; Table~\ref{tab:flow} accounts for
every exclusion between the full panel and that sample. The reduction is
driven almost entirely by generic requirements shared across methods
(forecaster training history, calibration warmup) and by the most
data-hungry \emph{baseline}: HAR quantile regression requires 800
observations per stock, and the common sample is exactly its usable set.
Our method and the conformal baselines are individually usable on
365{,}569--375{,}072 stock-days, and their full-sample results match the
common-sample results to within 0.2 points throughout, so the
intersection does not select in our favor. Seeds are fixed; every table
and figure regenerates from one driver script.

\begin{table}[t]
\centering
\caption{Sample flow (E2): from the full panel to the ten-method
common comparison sample. Each ``usable by'' row counts stock-days on
which that method produces a non-warmup interval.}
\label{tab:flow}
\small
\begin{tabular}{lr}
\toprule
Stage & Stock-days \\
\midrule
Full panel 2005--2025 & 519{,}843 \\
With point forecast and target & 394{,}213 \\
Usable by ACI / DtACI / SF-OGD / TCP-RM & 375{,}072 \\
Usable by KNN-state / XS-panel / pooled $K=1$ / RC (both) & 365{,}569 \\
Usable by HAR-QREG (800-day training minimum) & 269{,}705 \\
Common sample (intersection) & 269{,}705 \\
\bottomrule
\end{tabular}
\end{table}
