\section{Related work}\label{sec:related}

\paragraph{Online conformal prediction.}
Adaptive conformal inference (ACI) tracks a coverage target online through
distribution shift \citep{gibbs2021adaptive}; DtACI aggregates ACI experts
over a learning-rate grid \citep{gibbs2022conformal}, SF-OGD provides
strongly adaptive regret guarantees \citep{bhatnagar2023improved}, and
conformal PID control adds integrator and forecast terms
\citep{angelopoulos2023conformal}. AgACI \citep{zaffran2022adaptive},
EnbPI \citep{xu2021conformal}, HopCPT \citep{auer2023conformal}, and
weighted variants beyond exchangeability \citep{barber2023conformal} adapt
conformal prediction to temporal dependence. All of these target
\emph{marginal} coverage of a single stream; our starting exhibit is that
marginal validity is insufficient in exactly the states where volatility
intervals are consumed. Our adaptive-rate machinery builds directly on
DtACI, and our corrector has the quantile-tracking-plus-integrator
structure of conformal PID; the delta is that both operate per regime,
gated by online-estimated memberships, and are pooled across a panel.

\paragraph{Conditional and group-conditional coverage.}
Exact distribution-free conditional coverage is impossible in finite
samples \citep{foygelbarber2021limits}; practical work therefore targets
coverage over specified groups. Multivalid prediction achieves multi-group
validity in batch and adversarial settings \citep{bastani2022practical},
and \citet{bharti2026parameterfree} obtain parameter-free group-conditional
online conformal guarantees. In all of these the groups are \emph{given} to
the algorithm. Our regimes are estimated online from market data: the
guarantee necessarily conditions on the filtered estimate, and we quantify
the cost of that estimation both theoretically
(Remark~\ref{rem:estimated}) and with an oracle ablation
(Section~\ref{sec:oracle}). With hard, given regimes and fixed rates, our
tracker reduces to a group-conditional scheme in the spirit of this
literature; the reduction is exact and regression-tested.

\paragraph{Conformal methods in finance.}
A rapidly growing 2025--26 literature applies conformal calibration to
financial risk. \citet{schmitt2026taming} calibrates one-sided portfolio
VaR with recency and regime-similarity weights under weighted
exchangeability; \citet{aich2025temporal} combine quantile regression with
decaying-rate online conformal updates on index data;
\citet{proxyvar2026} recalibrate one-sided VaR with proxy-reliance
control; \citet{su2024adaptive} perform conformal inference for hidden
states of an HMM. Relative to this line, our setting is a cross-sectional
\emph{panel} of individual equities rather than a single portfolio or
index; our regimes are estimated online rather than supplied as features;
our target is regime-\emph{conditional} coverage rather than marginal; and
we evaluate conditionally throughout. \citet{lin2022conformal} and the
weighted panel extension of \citet{wtqa2026panel} pool calibration
information across cross-sectional units; similarity weighting appears in
our comparison as the KNN-state baseline, and Section~\ref{sec:results}
implements the two closest recent proposals directly, TCP-RM
\citep{aich2025temporal} and a cross-sectional split-conformal baseline
in the spirit of \citet{wtqa2026panel}, on the identical panel. Both are
marginally valid and both leave most of the stress deficit in place,
which is why our pooling operates inside regime-conditional tracking
loops instead. Table~\ref{tab:related} locates this paper against the
four nearest neighbours.

\begin{table}[t]
\centering
\caption{The four nearest methods and where this paper differs.
``Feedback'' means an online update driven by realized coverage errors.}
\label{tab:related}
\small
\begin{tabular}{lp{2.2cm}p{2.3cm}p{2.6cm}p{2.6cm}}
\toprule
 & Data setting & Regimes / groups & Coverage target & Evaluation \\
\midrule
\citet{bharti2026parameterfree} & single stream & given to algorithm &
group-conditional & synthetic + benchmark ML \\
\citet{aich2025temporal} & 3 index series & none &
marginal (feedback) & marginal + crisis window \\
\citet{wtqa2026panel} & generic panel & none (unit similarity) &
per-unit marginal & synthetic + small panels \\
\citet{proxyvar2026} & single portfolio & none &
one-sided marginal & VaR backtests \\
\addlinespace
This paper & 223-stock PIT panel & estimated online &
regime-conditional (feedback per regime) & conditional throughout +
VaR + TSFM repair \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Volatility and VaR econometrics.}
HAR regressions \citep{corsi2009simple} on realized measures
\citep{andersen2003modeling} remain the point-forecasting workhorse;
GARCH-$t$ \citep{bollerslev1986generalized} and CAViaR
\citep{engle2004caviar} are the canonical parametric and semiparametric
VaR models, and we evaluate against both with standard backtests
\citep{kupiec1995techniques, christoffersen1998evaluating}. Within the
International Journal of Forecasting, regime structure in volatility
forecasting is an active conversation: regime-switching GARCH-MIDAS
\citep{segnon2024forecasting}, deep switching state-space models
\citep{xu2026deep}, time-varying distributional shape of realized
volatility \citep{opschoor2023realized}, extreme-return quantile
forecasting \citep{tomlinson2024hawkes}, quantile-scale VaR/ES dynamics
\citep{liu2026quantile}, and forecasting after extreme observations
\citep{boug2026getting}. These papers model the volatility process or its
tails; we take any such forecaster as given and repair the conditional
validity of its uncertainty statements. The result is a complementary layer, not a
competing model. Our day-2 finding echoes \citet{boug2026getting}'s
evidence that forecasts struggle immediately after extreme observations,
sharpened here to a specific, quantified coverage limit.

\paragraph{Time-series foundation models.}
Zero-shot TSFMs such as Chronos \citep{ansari2024chronos}, TimesFM
\citep{das2024decoder}, and Moirai \citep{woo2024unified} are entering
forecasting practice, and recent evaluation in finance considers point
accuracy only, whether on realized volatility
\citep{brini2026forecasting} or on returns
\citep{noguer2026pretrained}. We add the
calibration dimension: Chronos-Bolt's native bands are directionally
miscalibrated in stress, and a conformal layer with regime pooling repairs
them at modest width cost. To our knowledge this is the first
regime-conditional calibration audit of a TSFM in finance.

\paragraph{The gap.}
No prior work combines online-\emph{estimated} regimes,
cross-sectional pooling of the calibration signal, regime-conditional
coverage targets with per-regime guarantees, one-sided VaR heads, and
foundation-model repair, all evaluated conditionally at panel scale. Each
element exists in isolation somewhere in the literature above; the
combination, and the phenomenon that motivates it, do not.
