\documentclass[review]{elsarticle}

\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{algorithm}
\usepackage{algpseudocode}

\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}

\biboptions{authoryear}

\journal{the International Journal of Forecasting}

\begin{document}

\begin{frontmatter}

% Working title — candidate 1 of the approved plan; final choice before submission.
\title{Regime-Conditional Conformal Prediction for Realized Volatility Forecasting}

\author[inst1]{Shivam Arora\corref{cor1}}
\ead{sarora01@villanova.edu}
\cortext[cor1]{Corresponding author.}

\author[inst1]{Venkat Margapuri}
\ead{venkatasivakumar.margapuri@villanova.edu}

\affiliation[inst1]{
  organization={Villanova University},
  addressline={Department of Computing Sciences},  % TODO: confirm exact department name with author
  city={Villanova},
  state={PA},
  country={United States}
}

\begin{abstract}
Uncertainty statements attached to volatility forecasts are consumed
conditionally --- on the bad days --- yet the methods that produce them
are validated on average. On a survivorship-bias-free panel of the 100
largest US stocks (2005--2025; 519{,}843 stock-days; point-in-time CRSP
universe), we show that online conformal prediction intervals for
next-day realized volatility are marginally valid but conditionally
broken: intervals promised at 90\% cover 83\% of stress-regime days and
over-cover calm ones, with the shortfall concentrated in the upper tail
that risk management consumes; a zero-shot time-series foundation model
(Chronos) exhibits the same failure directionally. We introduce a
regime-conditional calibration layer that wraps any forecaster: conformal
thresholds are maintained per market regime, estimated online; the
calibration signal is pooled across the cross-section, giving rare
regimes two orders of magnitude more updates than any single series
provides; and per-regime learning rates are set by online expert
aggregation with an issued-interval corrector, leaving no tuned
parameters. The layer removes most of the conditional deficit (stress
coverage 88.3\%) at no cost in average interval score (Model Confidence
Set), delivers the best stress-day Value-at-Risk backtests among seven
methods including GARCH-$t$ and CAViaR, repairs the foundation model's
bands, and carries finite-sample per-regime coverage guarantees valid
under arbitrary cross-sectional and serial dependence. One deficit
survives everything we tried, including option-implied signals and an
oracle given full-sample regime knowledge: coverage on the second day of
a volatility spike. We characterize this onset window as an open problem
for any backward-looking calibration scheme.
\end{abstract}

\begin{highlights}
\item Marginally valid conformal volatility intervals cover 83\% of
  stress days when 90\% is promised, across 21 years and 200+ stocks.
\item A regime-conditional, cross-sectionally pooled, self-tuning
  conformal layer removes most of the deficit at no average cost.
\item Finite-sample per-regime coverage guarantees hold under arbitrary
  serial and cross-sectional dependence.
\item The layer yields the best stress-day VaR backtests among seven
  methods and repairs a foundation model's miscalibrated bands.
\item Day-2-of-spike coverage resists all conditioning, including oracle
  regimes and option-implied signals --- an honest, quantified limit.
\end{highlights}

\begin{keyword}
Conformal prediction \sep Realized volatility \sep Regime switching \sep Uncertainty quantification \sep Value-at-Risk \sep Online learning
\end{keyword}

\end{frontmatter}

\input{sections/intro}
\input{sections/related}
\input{sections/method}
\input{sections/theory}
\input{sections/data}
\input{sections/results}
\input{sections/ablations}
\input{sections/onset}
\input{sections/conclusion}

\bibliographystyle{elsarticle-harv}
\bibliography{refs}

\end{document}
