% Separate title page for double-anonymized IJF submission.
% Build: latexmk -pdf titlepage.tex
\documentclass[11pt]{article}
\usepackage[margin=1.2in]{geometry}
\usepackage{microtype}
\begin{document}
\thispagestyle{empty}

\begin{center}
{\LARGE Regime-Conditional Conformal Prediction for Realized Volatility
Forecasting}

\vspace{2em}
{\large Shivam Arora$^{a,*}$ \quad Venkat Margapuri$^{a}$}

\vspace{1em}
$^{a}$Department of Computing Sciences, Villanova University,
Villanova, PA, United States

\vspace{0.5em}
$^{*}$Corresponding author. \textit{E-mail:} sarora01@villanova.edu
(S.~Arora); venkatasivakumar.margapuri@villanova.edu (V.~Margapuri).
\end{center}

\vspace{2em}
\noindent\textbf{CRediT authorship contribution statement.}
\textbf{Shivam Arora:} Conceptualization, Methodology, Software, Formal
analysis, Investigation, Data curation, Writing -- original draft,
Writing -- review \& editing, Visualization.
\textbf{Venkat Margapuri:} Supervision, Writing -- review \& editing.

\vspace{1em}
\noindent\textbf{Declaration of competing interest.}
The authors declare that they have no known competing financial
interests or personal relationships that could have appeared to
influence the work reported in this paper.

\vspace{1em}
\noindent\textbf{Funding.}
This research did not receive any specific grant from funding agencies
in the public, commercial, or not-for-profit sectors.

\vspace{1em}
\noindent\textbf{Declaration of generative AI use.}
During the preparation of this work the authors used Claude (Anthropic)
to assist with software development, literature search, and editing of
the manuscript text. After using this tool, the authors reviewed and
edited the content as needed and take full responsibility for the
content of the published article.

\vspace{1em}
\noindent\textbf{Data availability.}
Realized-volatility estimates are from the Chicago Booth Risk Lab;
universe construction uses CRSP via WRDS (license-restricted, not
redistributable); market state variables are from FRED and CBOE. Full
replication code, with fixed seeds and a single driver script that
regenerates every table and figure, accompanies the submission.

\end{document}
